Measurement Bias from Address Aliasing

### 2014-05-17 paper.tex
Update to 14.04
Plus minor adjustments in paper

% Include preview of aliasing program early to provike interest. 
% Also lightly referenced in introduction/background
\begin{lstlisting}[float=t, language=C, caption={Micro-kernel succeptible to aliasing between static and automatic variables depending on environment sizes}, label={lst:loopkernel}, frame=lines]
static int i, j, k;
int main() {
    int g = 0, inc = 1;
    for (; g < 65536; g++) {
        i += inc;
        j += inc;
        k += inc; 
    }
    return 0;
}
\end{lstlisting}

@@

Because bias can be hardware dependent, and to keep the scope of this work manageable, we choose to focus on the Intel ``Haswell'' microarchitecture specifically.
Our setup consists of a 4th generation Intel\textsuperscript{\textregistered} Core\textsuperscript{\texttrademark} i7-4770K processor, running 64-bit Ubuntu 13.10.
Code samples are compiled using the GCC toolchain, version 4.8.1-10ubuntu9.

@@

% \begin{table}[t]
%   \caption{Addresses returned by different heap allocators when allocating pairs of equally sized buffers}
%   \label{tab:mallocompare}
%   \centering
%   \small
%   \begin{tabular}{l r r}
%     \toprule
%                       & 5120 B          & $2^{20}$ B \\
%     \midrule
%     glibc             & 0x6028d0        & 0x2aaaaaaf3010 \\
%     (ptmalloc)        & 0x603ce0        & 0x2aaaab098010 \\
%     \midrule
%     tcmalloc          & 0xe16000        & 0xe64000 \\
%                       & 0xe18800        & 0xf64000 \\
%     \midrule
%     jemalloc          & 0x2aaaabc1f000  & 0x2aaaabc86000 \\
%                       & 0x2aaaabc21000  & 0x2aaaabd86000 \\
%     \midrule
%     Hoard             & 0x2aaaaab40070  & 0x2aaaabf40070 \\
%                       & 0x2aaaaab42070  & 0x2aaaac060070 \\
%     \bottomrule
%   \end{tabular}
% \end{table}

>>>>

% Include preview of aliasing program early to provike interest. 
% Also lightly referenced in introduction/background
\begin{lstlisting}[float=t, language=C, caption={Micro-kernel presented by Mytkowitz et al~\cite{Mytkowicz:2009:WrongData}, succeptible to bias from variations to system environment variables.}, label={lst:loopkernel}, frame=lines]
static int i, j, k;
int main() {
    int g = 0, inc = 1;
    for (; g < 65536; g++) {
        i += inc;
        j += inc;
        k += inc; 
    }
    return 0;
}
\end{lstlisting}

@@

Because bias can be hardware dependent, and to keep the scope of this work manageable, we choose to focus on the Intel ``Haswell'' microarchitecture specifically.
Our setup consists of a 4th generation Intel\textsuperscript{\textregistered{}} Core\texttrademark{} i7-4770K processor, running 64-bit Ubuntu 14.04 LTS on kernel version 3.13.0-24-generic.
Code samples are compiled using the {\small GCC} toolchain, version 4.8.2-19ubuntu1.

@@
